Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?

### 2022-10-05 Paper.Rmd
2nd draft minor fix

This study collected Online Customer Reviews data from two different sources (IMDB and BestBuy) and analyzed the data within the context of consumer uncertainty. Negativity Bias Theorem, Prospect Theory and Search / Experience goods paradigm from information economics were used as an theoretical engine to explain the information gathering process of a consumer. Results showed similarities from the existing Review Helpfulness literature. However, once again it should be noted that the literature has many conflicting results.

@@

There are some implications for future studies. Firstly, aside from lexicon based sentiment analysis it is also possible to utilize deep learning methods to mine opinions from a text. One advantage of deep learning method over a lexicon is its versatility. A negative word can change from one context to another and training a deep learning method is more robust to this type of contextual changes whereas with lexicons a negative word is a negative word no matter the context is. Next, future studies should consider collecting data from different regions and cultures. There might be some differences on how consumers process and react to the information in order to deal with uncertainty. Additionally, researchers can dig deeper into search and experience goods paradigm. It is well established in the literature that product type affects the information gathering process. However, there might be differences within product types depending on their search and experience attributes. An objective way to identify and index experience and search attributes may also shed some light to the conflicting results in the literature. Lastly, since Online Customer Reviews data is ever growing more researchers should incorporate Exploratory Data Analysis into their works. Reviews and how helpful these reviews are perceived from potential buyers is relatively a new topic. In addition, new ways to analyze text data are being developed so Online Customer Reviews offer a great potential for new discoveries from the data. This increases the value of EDA as well.

>>>>

This study collected Online Customer Reviews data from two different sources (IMDB and BestBuy) and analyzed the data within the context of consumer uncertainty. Negativity Bias Theorem, Prospect Theory and Search / Experience goods paradigm from information economics were used as an theoretical engine to explain the information gathering process of an average consumer. Results showed similarities from the existing Review Helpfulness literature. However, once again it should be noted that the literature has many conflicting results.

@@

There are some implications for future studies. Firstly, aside from lexicon based sentiment analysis it is also possible to utilize deep learning methods to mine opinions from a text. One advantage of deep learning method over a lexicon is its versatility. A negative word can change from one context to another and training a deep learning method is more robust to this type of contextual changes whereas with lexicon based methods a negative word is a negative word no matter the context is. Next, future studies should consider collecting data from different regions and cultures. There might be some differences on how consumers process and react to the information in order to deal with uncertainty. Additionally, researchers can dig deeper into search and experience goods paradigm. It is well established in the literature that product type affects the information gathering process. However, there might be differences within product types depending on their search and experience attributes. An objective way to identify and index experience and search attributes may also shed some light to the conflicting results in the literature. Lastly, since Online Customer Reviews data is ever growing more researchers should incorporate Exploratory Data Analysis into their works. Reviews and how helpful these reviews are perceived by potential buyers is relatively a new topic. In addition, new ways to analyze text data are being developed so Online Customer Reviews offer a great potential for new discoveries from the data. This increases the value of EDA as well.
